---
title: "Emei"
documentclass: ctexart
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: '4'
  rticles: ctex
classoption: landscape
header-includes: \usepackage{longtable}
params:
  all_rec: NA
  data.path: NA
  checks.path: NA
  mystudy: NA
  mycat: NA
  mypriority: NA
  myserver: NA
  cwd: NA
---

```{r, echo=FALSE}
# The `params` object is available in the document.
# making its items to be available for the rest of the code

all_rec <- params$all_rec
mystudy <- params$mystudy
mycat <- params$mycat
mypriority <- params$mypriority
myserver <- params$myserver
data.path <- params$data.path
checks.path <- params$checks.path

### Get system time to print to document
mytime <- as.character(as.POSIXct(format(Sys.time(), tz = "Asia/Shanghai", usetz = TRUE)))

#### Get MedDRA version
#### ts conflits with R function ts so need to check if it is data instead
#### of does not exist
if (!(exists("ts") & "data.frame" %in% class(ts))) {
  mymeddra <- "TS Not Found"
} else {
  mymeddra0 <- subset(ts, ts$TSPARMCD == "AEDICT", grepl("TSVAL", names(ts)))
  if (nrow(mymeddra0) > 0) {
    mymeddra <- as.character(mymeddra0)
    mymeddra <- subset(mymeddra, mymeddra != "")
  } else {
    mymeddra <- "Not Found"
  }
}

options(tibble.print_max = Inf)
options(tibble.width = Inf)
```

\newpage

## Study Info, Assumptions, and Caveats

### Study Info

-   Server: `r myserver`
-   Study: `r mystudy`
-   Check Type: `r mycat`
-   Check Priority: `r mypriority`
-   MedDRA Version: `r mymeddra`
-   Data Location: `r data.path`
-   Date/Time Report Generated: `r paste(mytime,"Beijing Time")`

### Package Info

-   [Click here for a link to the `Emei` package public site](https://github.com/Pharma-Mountain-High/emei)

### Assumptions

-   These checks look for common SDTM data issues encountered by study teams 
-   Data is assumed to follow SDTMv standards
-   Data is assumed to be saved as an uncompressed .sas7bdat files

### Caveats

-   ***For blinded studies, please be cautious of potential unblinding when sharing this report***
-   These checks are not comprehensive so some data issues may not be reported
-   Some checks may report false positives due to study specific differences
-   This report is meant to supplement, not replace, running Pinnacle 21 (P21) on SDTM. P21 should still be run early and often

### Report generated via [Pharma-Mountain-High/emei](https://github.com/Pharma-Mountain-High/emei)

\newpage

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
varsthatneedcleaning <- c("AETERM", "CMTRT", "CMINDC", "CMDECOD", "DSTERM", "DVREAS", "LBORRES", "PRINDC", "PRTRT", "RSORRES", "VISIT", "last.vis")
MAX_COLS <- 10 # max columns per table in landscape layout
KEY_COLS <- 2 # number of leading key columns to repeat in each split part
mycnt2 <- 0

for (i in 1:length(all_rec)) {
  mycnt2 <- mycnt2 + 1

  # ignore incProgress() when running outside Shiny app
  if (shiny::isRunning() == TRUE) {
    incProgress(1, detail = paste(mycnt2, "of", length(all_rec)))
  }


  cat("  \n##", as.character(metads[metads$check == names(all_rec)[i], "pdf_title"]), " \n")
  cat("### Study", mystudy, " \n")
  # cat("### Date/Time Generated:", mytime, " \n" )
  cat("  \n", as.character(metads[metads$check == names(all_rec)[i], "pdf_subtitle"]), " \n")
  # cat("  \n")


  myattrib <- all_rec[[i]]

  ###
  # Add a note that records are truncated to 50 as needed
  ###

  if ("data" %in% names(myattrib) & nrow(myattrib$data) > 50) {
    if (identical(myattrib$msg, character(0))) {
      myattrib$msg <- ""
    } # in case message wasn't set
    myattrib$msg <- paste(myattrib$msg, "More than 50 records found, only first 50 records displayed.  Please run the Excel report to obtain all records.")
  }

  ###
  # Output
  ###

  if ("data" %in% names(myattrib) & nrow(myattrib$data) > 0) {
    # Remove long flag variable from PDF
    myattrib$data <- myattrib$data %>%
      select(-any_of("check_stat"))

    # Convert certain problem vars to ASCII to avoid latex issues
    # Also truncate them when they are long (e.g >50)

    vars_to_be_cleaned <- intersect(varsthatneedcleaning, names(myattrib$data))
    if (length(vars_to_be_cleaned) > 0) { # check if any vars need to be cleaned

      # Add a note re: ascii conversion and truncation
      # if(identical(myattrib$msg,character(0))){myattrib$msg=""}#in case message wasn't set

      # myattrib$msg = paste(myattrib$msg,
      # "Note: The following variables may have been modified in this report to improve display:",
      # paste(vars_to_be_cleaned,collapse=",")
      # )

      cat(
        "  \n", "* Note: The following variables may have been truncated in this report to improve display:",
        paste(vars_to_be_cleaned, collapse = ","), " \n"
      )

      for (cleanthisvar in vars_to_be_cleaned) { # iterate over each variable that needs to be cleaned

        # 只进行截断，不再转换为ASCII字符
        myattrib$data <- truncate_var_strings(dt = myattrib$data, var_name = cleanthisvar, trunc_length = 50) # truncate var at 50 characters
      } # end of for iterating over each var to be cleaned
    } # end of if checking for any vars

    # Print the fail message
    cat("\n\n", paste0("**", myattrib$msg, "**", col.names = ""))

    # Print check results (limited to 50 recs)
    df <- head(myattrib$data, 50)

    if (ncol(df) <= MAX_COLS) {
      print(
        knitr::kable(df, row.names = FALSE, longtable = TRUE, format = "latex") %>%
          kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 8, position = "left")
      )
    } else {
      # Split wide table into column chunks, repeating the first KEY_COLS columns
      key_idx <- seq_len(min(KEY_COLS, ncol(df)))
      rest_idx <- seq(KEY_COLS + 1, ncol(df))
      chunk_w <- MAX_COLS - length(key_idx)
      chunks <- split(rest_idx, ceiling(seq_along(rest_idx) / chunk_w))
      n_parts <- length(chunks)

      for (p in seq_len(n_parts)) {
        col_idx <- if (p == 1) seq_len(MAX_COLS) else c(key_idx, chunks[[p]])
        col_idx <- col_idx[col_idx <= ncol(df)]
        sub_df <- df[, col_idx, drop = FALSE]

        cat(sprintf("\n\n**(Part %d / %d)**\n\n", p, n_parts))
        print(
          knitr::kable(sub_df, row.names = FALSE, longtable = TRUE, format = "latex") %>%
            kableExtra::kable_styling(latex_options = c("repeat_header"), font_size = 8, position = "left")
        )
      }
    }
  } else if (!identical(myattrib$msg, character(0))) { # Fail message exists but no associated data
    cat("\n\n", paste0("**", myattrib$msg, "**"))
  } else if (trimws(myattrib$notes) != "") { # Check not run due to missing domain
    cat("\n\n", paste0("**", gsub("ATTENTION! ", "", myattrib$notes), "**"))
  } else {
    cat("\n\n", paste0("**", "No issues detected", "**"))
  }



  cat("  \n")
  cat("\n\n\\pagebreak\n")
}
```
